\subsubsection{Experience}\label{experience}

\paragraph{Senior Informatics Analyst, University of Oklahoma; Norman,
OK
\textbf{2010-present}}\label{senior-informatics-analyst-university-of-oklahoma-norman-ok-2010-present}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Built a team of informatics professionals by embedding with and
  partnering with research faculty to provide enabling
  cyber-infrastructure for global environmental change research
  projects.
\item
  Architect and implement open source software/hardware solutions for
  research orientated BigData workflows.
\item
  Develop and deliver teaching and training material, advancing
  scientific throughput through appropriate use of software systems and
  tools.
\item
  Active participant in grant writing to build soft-money funded
  research-support operation bringing in over \$2.9m per year in federal
  research dollars, covering in excess of \$300k per year in salary for
  the Informatics services team.
\end{itemize}

\paragraph{Senior Analyst, Lanworth; Itasca, IL
\textbf{2008-2010}}\label{senior-analyst-lanworth-itasca-il-2008-2010}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Led quantitative analysis team, using satellite remote sensing,
  biophysical crop modeling and exploratory data analysis techniques to
  quantify corn, soy and wheat production in the USA, Brazil, Argentina
  and Black Sea states.
\item
  Acted as project manager and assisted with business development for
  major consulting contracts, building the firm to over \$5-million in
  annual revenue.
\item
  The firm is now a wholly owned subsidiary of Thomson Reuters.
\end{itemize}

\paragraph{Graduate Research Assistant, Purdue University; West
Lafayette, IN
\textbf{2005-2008}}\label{graduate-research-assistant-purdue-university-west-lafayette-in-2005-2008}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Studied impacts of land-use change on ecosystem services, specifically
  studying land use change dynamics in the Muskegon River Watershed area
  of Michigan coupled to ecological response models.
\item
  Acted as Linux/Windows system administrator of computational
  infrastructure in the Human Environment Modeling and Analysis (HEMA)
  Laboratory.
\end{itemize}

\paragraph{Partner, International Technology Strategy Partners;
Lafayette, IN
\textbf{2002-2007}}\label{partner-international-technology-strategy-partners-lafayette-in-2002-2007}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Co-founded a niche consultancy that facilitated workshops for shared
  visioning of technology futures at global high tech organizations.
\item
  Provided consulting and educational services to Fortune 100 companies,
  federal agencies, DoD and global universities.
\end{itemize}

\paragraph{Strategic Planning and Center Coordinator, Purdue
Univerisity; Lafayette, IN
\textbf{2001-2005}}\label{strategic-planning-and-center-coordinator-purdue-univerisity-lafayette-in-2001-2005}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Internal consultant to support Deans and VPs with their strategic
  planning and future visioning during a major strategic planning cycle.
\item
  Later became a strategic advisor to the University CIO while operating
  an academic center for best practices in Technology Roadmapping.
\end{itemize}
